### 2017-09-27 TF-vldb2018/sec-tsimAlg.tex

\revise{
\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1). 
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the incremental algorithm in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11, see~\cite{fullvldb18}).}
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

>>>>

\revise{
\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1). 
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).}
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.
